Creating optimal conditions for reproducible data analysis in R with `fertile`

### 2020-03-16 fertile.Rmd
more citations and edits

Reproducibility is critically important to the advancement of knowledge in
all fields of scientific research. Researchers are acknowledging this; 
publications and discussions focusing on reproducibility seem to have 
increased in frequency over the last several years (@sep-scientific-reproducibility), (@plos-biology), (@bioessays-gosselin)

@@

Much of the available literature focuses on file structure, organization, 
and naming, and **fertile**'s features are consistent with this. The 
*ideal* file structure is not agreed upon by academics, though there are 
some recommendations focused on R that are available. @marwick2018packaging
provides the framework for file structure that **fertile** is based on: a 
structure similar to that of an R package [**Cite Hadley's Writing R 
Packages and the R Core Team's Writing R Extensions**], with an `R` 
folder, as well as `data`, `data-raw`, `inst` and `vignettes`.

>>>>

Reproducibility is critically important to the advancement of knowledge in
all fields of scientific research. Researchers are acknowledging this; 
publications and discussions focusing on reproducibility seem to have 
increased in frequency over the last several years [@sep-scientific-reproducibility, @plos-biology, @bioessays-gosselin, @eisner-reproducibility, @engineering-reproducibility].

@@

Much of the available literature focuses on file structure, organization, 
and naming, and **fertile**'s features are consistent with this. The 
*ideal* file structure is not agreed upon by academics, though there are 
some recommendations focused on R that are available. @marwick2018packaging
provides the framework for file structure that **fertile** is based on: a 
structure similar to that of an R package (@hadley-packages, @coreteam-extensions),
with an `R` folder, as well as `data`, `data-raw`, `inst` and `vignettes`.
